Dotted Suffix Trees\\A Structure for Approximate Text Indexing

### 2005-09-03 paper/construction.tex
I like $\mathcal{O}$ for big-O notation
Small corrections

For any other node $\overline{aw}$, the error tree is a filtered copy of the error tree at node $\overline{w}$ (the node pointed to by node $\overline{aw}$'s suffix link.

\begin{enumerate}
\item The leaf labeled 1 in the original error tree is not included
\item A leaf labeled $p$ is only included if $s_{p-1}$ is $a$ (the label of the suffix link)
\item All leafs in the copy have a label which is the original label's value minus one
\end{enumerate}

@@

\begin{figure}
\includegraphics{merge}
\caption{Node Merging demonstration}%
\label{fig:merge}
\end{figure}

@@

If the number of nodes in the final tree is $N$ and the alphabet $\Sigma$, then the above algorithm runs in time $O(N|\Sigma|)$.

@@

To construct the (k+1)-error tree from the k-error tree, make a copy of the tree as above (adjusting leafs and filtering the leafs labeled one) and make this the new root error tree. Then, for every other node, remove the current error tree (it has a level too few). Finally, for every node except the root, construct its error tree as above (adjusting leafs, filtering the leafs labeled one or which do not correspond to positions in the suffix link's label). These error trees will now have the correct number of nodes.

@@

>>>>

For any other node $\overline{aw}$, the error tree is a filtered copy of the error tree at node $\overline{w}$ (the node pointed to by node $\overline{aw}$'s suffix link).

\begin{enumerate}
\item The leaf labeled 1 in the original error tree is not included
\item A leaf labeled $p$ is included only if $s_{p-1}$ equals $a$ (the label of the suffix link)
\item All leafs in the copy have a label which is the original label's value minus one
\end{enumerate}

@@

\begin{figure}
\centering
\includegraphics[width=.5\textwidth]{merge}
\caption{Node Merging demonstration}%
\label{fig:merge}
\end{figure}

@@

If the number of nodes in the final tree is $N$ and the alphabet $\Sigma$, then the above algorithm runs in time $\mathcal{O}(N|\Sigma|)$.

@@

To construct the (k+1)-error tree from the k-error tree, make an adjusted copy of the tree as above (adjusting leafs and filtering the leafs labeled one) and make this the new root error tree. Then, for every other node, remove the current error tree (it has a level too few). Finally, for every node except the root, construct its error tree as above (adjusting leafs, filtering the leafs labeled one or which do not correspond to positions in the suffix link's label). These error trees will now have the correct number of nodes.

@@

The analysis for the time cost above remains valid. Taking $N_i$ to mean the number of nodes of the i-error tree, we now have that the time cost is $\mathcal{O}(N_1|\Sigma|+N_2|\Sigma|+\dots+N_k|\Sigma)=\mathcal{O}((N_1+N_2+\dots+N_k)|\Sigma|)=\mathcal{O}(N_k|\Sigma|)=\mathcal{O}(N|\Sigma|)$ since $N_k \le N_i$ ($N_k = N$).
